Developing a preprint culture in biology

### 2012-09-28 ms.tex
typo

PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
needs a license identical to the license that governs the original work.

>>>>

PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
by Figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
need a license identical to the license that governs the original work.
